---
output:
  html_document:
    css: ~/knitr.css
    fig_caption: yes
    highlight: default
    keep_md: yes
    number_sections: no
    theme: journal
    toc: no
---

knitr skeleton

```{r setup, echo = TRUE, message=FALSE}
## project directory
projdir <- '~/Documents/r.packages/knitr/'
filename <- 'knitr_skeleton'


## files: 
## 00-master.Rmd
## 00-surv.Rmd

## all packages to load:
library(Gmisc)
library(rawr)
```

<font color = red>
NOTES:    
some things to do

</font>

```{r knitr, include=FALSE}
library(knitr)
## package options
opts_knit$set(eval.after = 'fig.cap', ## to use chunk results in the fig.cap,
                                      ## evaluate captions after chunk
              progress = TRUE, 
              width = 80, 
              verbose = TRUE, 
              par = TRUE)
              
## global chunk options:
opts_chunk$set(warning = TRUE, 
               message = TRUE,
               cache = FALSE,     # cache chunks for faster compiles
               tidy = FALSE,      # respect code formatting
               echo = TRUE,       # show/hide code
               dev = 'CairoPNG',  # device options (install.packages('Cairo'))
               dev.args = list(antialias = 'none',
                               bg = 'transparent'), 
               dpi = 96,
               fig.path = 'figure/',   # default
               cache.path = 'cache/',  # default
               fig.align = 'center')
## more http://yihui.name/knitr/options

## customizable functions to run before/after a code chunk 
## and tweak the output of knitr 
## more info: http://yihui.name/knitr/hooks
knit_hooks$set(par = function(before, options, envir) {
                 ## par settings
                 # tune details of base graphics (http://yihui.name/knitr/hooks)
                 if (before && options$fig.show != 'none') 
                   par(mar = c(4,4,.1,.1), 
                       cex.lab = .95,
                       cex.axis = .9, 
                       mgp = c(2,.7,0),
                       tcl=-.3)
                 },
               plot = function(x, options) {
                 ## plot settings
                 fig_fn = paste0(opts_knit$get('base.url'),
                                 paste(x, collapse = '.'))
                 fig.cap <- knitr:::.img.cap(options)
                 style = c('display:block',
                           sprintf('margin: %s;',
                                   switch(options$fig.align,
                                          left = 'auto auto auto 0',
                                          center = 'auto',
                                          right = 'auto 0 auto auto')))
                 addon_args <- ''
                 fig_number_txt <- ''
                 cntr <- getOption('figure_counter', FALSE)
                 if (cntr != FALSE) {
                   if (is.logical(cntr))
                     cntr <- 1
                   ## figure_counter_str allows for custom figure text, 
                   ## eg, <b> Figure %s:</b>
                   ## the %s allows for setting the counter manually to 1a, 1b, 
                   ## etc if needed
                   fig_number_txt <- 
                     sprintf(getOption('figure_counter_str', 'Figure %s: '),
                             ifelse(getOption('figure_counter_roman', FALSE),
                                    as.character(as.roman(cntr)), 
                                    as.character(cntr)))
                   if (is.numeric(cntr))
                     options(figure_counter = cntr + 1)
                   }
                 paste0("<figure><img src='", fig_fn, "'"," ", addon_args,
                        paste0(" style='", paste(style, collapse = '; '), 
                               "'"),'>',
                        '<figcaption>', fig_number_txt, fig.cap, 
                        '</figcaption></figure>')
                 })

## general settings 
options(figure_counter = TRUE,
        figure_counter_roman = TRUE)

## fonts for images
library(Cairo)
CairoFonts(regular = 'Calirbi:style=Regular',
           bold = 'Calirbi:style=Bold',
           italic = 'Calibri:style=Italic',
           bolditalic = 'Calibri:style=Bold Italic,BoldItalic',
           symbol = 'Symbol')

## table/figure counter and anchor formatter
#
## inc_num('table') or inc_num('figure') to increase the counter
## after each table or figure made
#
## get_num('table') or get_num('figure') to get the current number
## figure defaults to options('figure_counter_roman')
## use link = 'link1' to link to anchor 'link1' 
## link defaults to t1 or f1 for table or figure + respective count

figurenum_ <- 1
tablenum_ <- 1

inc_num <- function(which = c('table','figure')) {
  if (which == 'table')
    tablenum_ <<- tablenum_ + 1
  if (which == 'figure')
    figurenum_ <<- figurenum_ + 1
}

get_num <- function(which = c('table','figure'), link = NULL, 
                    roman = getOption('figure_counter_roman')) {
  upcase <- function(x) 
    paste0(toupper(substr(x, 1, 1)), substring(x, 2), collapse = ' ')
  num <- ifelse(which %in% 'table', tablenum_, figurenum_)
  alink <- sprintf('%s%s', ifelse(which == 'table', 't', 'f'), num)
  if (which == 'figure' && roman) 
    num <- as.roman(num)
  zzz <- sprintf('%s %s', upcase(which), num)
  if (!is.null(link)) {
    if (is.logical(link) && link)
      sprintf('[%s](#%s)', zzz, alink)
    else 
      sprintf('[%s](#%s)', zzz, link)
  }
  else zzz
}
```

<font align = center>

#### knitr skeleton

Description: a knitr template to use for documents.

Most recent compile: `r as.character(format(Sys.Date(), format = '%d %B %Y'))`

Department of Something   
Some Place

Statisticians:    
First Last, <a href="mailto:handle@site.edu?subject=subject">email address</a>

<font size = 1>
All analyses were performed using `r R.Version()$version.string` and packages `Gmisc` v`r packageVersion('Gmisc')` for table output ; `rawr` v`r packageVersion('rawr')` ([source](https://github.com/raredd/rawr)), a personal package with helper tools; and `knitr` v`r packageVersion('knitr')` [Xie, 2013] for reproducible research.

</font></font>

#### Table of contents   
\* [Outline](#outline)   
\* [Introduction](#intro)    
\* [Statistical methods](#stats)     
\* [Results](#results)  
\* [Discussion](#discuss)   
\* [References](#ref)   

----

#### <a id = "outline">Outline</a>

1. Abstract
2. Intro
3. Stats
4. Results
    + [Table 1: Patient demographics.](#t1)    
    + [Table 2: Some table.](#t2)    
    + [Figure 1: Some example plots.](#f1)   
    + [Figure 2: Some more example plots.](#f2)   
5. Discussion 
6. References

#### Abstract
*PURPOSE:* This study has some purpose.
*PATIENTS & METHODS:* We obtained some patients from somewhere, and some statistical things were done.
*RESULTS:* There were some results that may be interesting.
*CONCLUSION:* Conclude: it is as we said.

#### <a id = 'intro'>Introduction</a>
Description of the study. **Primary** objectives and **secondary** objectives.

#### <a id = 'stats'>Statistical methods</a>
We did some specific statistical methods.

Analyses were performed using `r R.Version()$version.string`.

#### <a id = 'results'>Results</a>
Results go here.

`r get_num('table', link = TRUE)` shows the patient characteristics.

<a id='t1'></a>
```{r table 1, results='asis'}
describeMedian_minmax <- function(...) describeMedian(..., iqr = FALSE)

## t1 wrapper function 1
getT1stat <- function(varname, digits = 0) {
  getDescriptionStatsBy(data[ , varname],
                        data$treat,
                        add_total_col = TRUE, 
                        show_all_values = TRUE,
                        hrzl_prop = FALSE,
                        statistics = FALSE,
                        html = TRUE,
                        digits = digits,
                        continuous_fn = describeMedian_minmax)
}

## some sample data
set.seed(1618)
f <- function(...) sample(..., 100, replace = TRUE)
data <- data.frame(age = rpois(100, 50),
                   cat_var = f(LETTERS[1:5]),
                   sex = f(c('Male','Female')),
                   race = f(c('Black','White','Asian')),
                   treat = factor(f(1:3), labels = c('Treatment A', 
                                                     'Treatment B', 
                                                     'Placebo')))
data <- within(data, {
  age_cat <- cut(age, c(-Inf, 40, 50, 60, Inf), labels = c('&le; 40','41 - 50',
                                                           '51 - 60','60 +'))
})

## table 1 stats
table_data <- list()
table_data[['Age']] <- rbind(getT1stat('age', digits = 1),
                             getT1stat('age_cat', digits = 1))
table_data[['Some categorical<br>&nbsp;&nbsp;variable']] <- getT1stat('cat_var')
table_data[['Sex']] <- getT1stat('sex')
table_data[['Race']] <- getT1stat('race')

## merge everything into a matrix 
## (matrices are preferred since they allow for duplicated rownames)
## create the rgroup & n.rgroup variables automatically
output_data <- do.call(rbind, table_data)
rgroup <- names(table_data)
n.rgroup <- unname(sapply(rgroup, function(x) nrow(table_data[[x]])))

# add a column spanner for the status columns
cgroup <- c("", "Type of treatment<sup>&dagger;</sup>")
n.cgroup <- c(1, 3) 
colnames(output_data) <- 
  c(paste0('Total<br><font weight = normal; size = 1>n = ',
           nrow(data), '</font>'),
    paste0('Treated A<br><font weight = normal; size = 1>n = ',
           sum(data$treat == 'Treatment A'),'</font>'),
    paste0('Treatment B<sup>&Dagger;</sup><br><font weight = normal; size = 1>n = ',
           sum(data$treat == 'Treatment B'),'</font>'),
    paste0('Placebo<br><font weight = normal; size = 1>n = ',
           sum(data$treat == 'Placebo'),'</font>'))


## create table with Gmisc package
inc_num('table')
htmlTable(output_data, align = 'rccc',
          rgroup = rgroup, n.rgroup = n.rgroup, 
          rgroupCSSseparator = '', 
          cgroup = cgroup,
          n.cgroup = n.cgroup,
          rowlabel = '', 
          ctable = TRUE, # latex-style table lines
          caption = "Table 1: Patient demographics", 
          altcol = c('grey97', 'white'),
          tfoot = paste0(
            "<font size=1>Abbreviations: ECOG, Eastern Cooperative Oncology Group;
            PS, performance score<br>
            <sup>&dagger;</sup>Trial groups for a new wonder drug<br>
            <sup>&Dagger;</sup> Twice the dosage of treatment A</font>"))
```

We can use an in-line chunk and caluclate the median age (`r median(data$age)`) without writing the number in myself! We define the median as

$$\operatorname{P}(X\leq m) \geq \frac{1}{2}\text{ and }\operatorname{P}(X\geq m) \geq \frac{1}{2}$$ for any $m \in \mathbb{R}$.

Here are some figures we generated in `r get_num('figure', link = TRUE, roman = TRUE)`.

<a id='f1'></a>
```{r f1, fig.cap='Some example plots', fig.height=5, fig.width=5}
op <- par(no.readonly = TRUE)
par(mar = c(3,3,2,1), oma = c(0,0,0,0),
    mfrow = c(2,2), xpd = FALSE, 
    cex.lab = .8, cex.main = .8, cex.axis = .8, las = 1)
inc_num('figure')
hist(mtcars$mpg)
boxplot(mpg ~ cyl, data = mtcars)
barplot(table(mtcars$am, mtcars$gear))
plot(mtcars$mpg)
box('outer')
```

As we saw in Figure `r as.character(as.roman(figurenum_ - 1))`, something something, and we can also see in `r get_num('figure', link = TRUE, roman = TRUE)`, something.

<a id='f2'></a>
```{r f2, fig.cap='Some example plots', fig.height=5, fig.width=5}
par(mar = c(3,3,2,1), oma = c(0,0,0,0),
    mfrow = c(2,2), xpd = FALSE, 
    cex.lab = .8, cex.main = .8, cex.axis = .8, las = 1)
fit <- lm(mpg ~ wt, data = mtcars)
inc_num('figure')
plot(fit, cex.id = .5, cex.caption = .8)
box('outer')
```

And we will also check the table counter in `r get_num('table', link = TRUE)`.

<a id='t2'></a>
```{r t2, results='asis'}
inc_num('table')
htmlTable(mtcars[1:10, ], caption = 'Table 2: Some table.')
```

### <a id = 'discuss'>Discussion</a>
Those were the results; now here are the implications.

### <a id = 'ref'>References</a>
Reference, First. "Article title." *Title of journal.* 2014.

```{r, results='asis'}
## packages
print(citation(package = 'Gmisc'), style = 'html')
## r citation
print(citation(), style = 'html')
```

---

```{r, echo = TRUE}
sessionInfo()
```

```{r copy, include = FALSE, cache = FALSE, eval = FALSE}
## have file save itself to report directory named as current day/month/year
pathr <- sprintf('%s%s.Rmd', projdir, filename)
pathh <- sprintf('%s%s.html', projdir, filename)
path_newr <- sprintf('%sreports/%s.Rmd',
                     projdir,
                     as.character(format(Sys.Date(), format = '%d%b%Y')))
path_newh <- sprintf('%sreports/%s.html',
                     projdir,
                     as.character(format(Sys.Date(), format = '%d%b%Y')))
file.copy(pathr, path_newr, overwrite = TRUE)
file.copy(pathh, path_newh, overwrite = TRUE)
```

```{r, eval=FALSE}
## knit in console:
knitr::knit(sprintf('%s%s.Rmd', projdir, filename), encoding = 'UTF-8')
## convert to html
knitr::knit2html(sprintf('%s%s.Rmd', projdir, filename))
## open in default browser
browseURL(sprintf('%s%s.html', projdir, filename))
```